Turbo fast no compromise gravitational wave parameter estimation

### 2022-12-12 src/tex/ms.tex
Finish heterodyned likelihood section.

We give a concise description of what we implement
in our code here. For more extensive discussion of the derivation of heterodyned
likelihood, we refer the reader the reference \cite{Zackay:2018qdy}.

@@

where $b$ denotes the index of a \textit{sparse} set of bins where the integrand
will be computed on, $A_0(b)$, $A_1(b)$, $B_0(b)$, and $B_1(b)$ are the
coefficients of computed using the data and the reference waveform, and
$r_0(h,b)$ and $r_1(h,b)$ are the ratio between the target waveform and the
reference waveform at the center of the bin. To evaluate eq. \ref{eq:
heterodynedlikelihood}, we need to be able to first choose a binning scheme,
evaluate the coefficients given the data and the reference waveform, and finally
evaluate the ratio between the target waveform and the reference waveform at the
center of the bin.

@@

\begin{align}
    A_0(b) &= 4 \sum_{f \in b} \frac{d(f)h^*_0(f)}{S_n(f)} df, \\
    A_1(b) &= 4 \sum_{f \in b} \frac{d(f)h^*_0(f)(f-f_m(b))}{S_n(f)} df, \\
    B_0(b) &= 4 \sum_{f \in b} \frac{|h_0(f)|^2}{S_n(f)} df, \\
    B_1(b) &= 4 \sum_{f \in b} \frac{|h_0(f)|^2(f-f_m(b))}{S_n(f)} df,
\end{align}

>>>>

We give a concise description of what we implement
in our code here. For more extensive  derivation of heterodyned
likelihood, we refer the reader the reference \cite{Zackay:2018qdy}.

@@

where $b$ denotes the index of a \textit{sparse} set of bins where the integrand
will be computed on, $A_0(b)$, $A_1(b)$, $B_0(b)$, and $B_1(b)$ are the
heterodyning coefficients computed using the data and the reference waveform,
and $r_0(h,b)$ and $r_1(h,b)$ are the ratio between the target waveform and the
reference waveform at the center of the bin. To evaluate eq. \ref{eq:
heterodynedlikelihood}, we need to be able to first choose a binning scheme,
then evaluate the coefficients given the data and the reference waveform and the
ratio between the target waveform and the reference waveform at the center of
the bin.

@@

The final ingredient we need is the heterodyning coefficients given the data and
the reference waveform on the sparse bins, which are given by
\begin{align}
    A_0(b) &= 4 \sum_{f \in b} \frac{d(f)h^*_0(f)}{S_n(f)} df, \\
    A_1(b) &= 4 \sum_{f \in b} \frac{d(f)h^*_0(f)(f-f_m(b))}{S_n(f)} df, \\
    B_0(b) &= 4 \sum_{f \in b} \frac{|h_0(f)|^2}{S_n(f)} df, \\
    B_1(b) &= 4 \sum_{f \in b} \frac{|h_0(f)|^2(f-f_m(b))}{S_n(f)} df.
\end{align}
Note that the sum within each bins should be done with the same sampling rate as
the data, i.e. the same one would do in the case without using heterodyned
likelihood.
